Simulations

### 2018-07-27 3-simus.Rmd
save

n <- nrow(G)
ind.HLA <- snp_indLRLDR(CHR, POS, subset(LD.wiki34, ID == "hild12"))

TTree <- "../TTree-source/TTree"

NCORES <- nb_cores()
```

@@

  # Get results from all methods
  res <- bind_rows(
    # PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple"),
    ttrees("../TTree-source/TTree", "backingfiles/ttrees", 
           pheno.all, ind.train, ind.test, n.trees = 100)
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```

>>>>

n <- nrow(G)
ind.HLA <- snp_indLRLDR(CHR, POS, subset(LD.wiki34, ID == "hild12"))
```

@@

  # Get results from all methods
  res <- bind_rows(
    # PRS(G, CHR, POS, pheno.all, covar.all, ind.train, ind.test),
    logit.CMSA(G,  pheno.all, covar.all, ind.train, ind.test, "logit-simple"),
    # logit.CMSA(G2, pheno.all, covar.all, ind.train, ind.test, "logit-triple"),
    ttrees("../TTree-source/TTree", "backingfiles/ttrees", 
           pheno.all, ind.train, ind.test, n.trees = 100)
  )
  params[["res"]] <- list(res)
  saveRDS(unnest(params, res, .drop = FALSE), file = res.file)
}
```
